---
title: "Brownlows Bets"
author: "Erica Sanchez!"
date: "10/16/2019"
output: html_document: default
 ---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```
### 'r as.character(Sys.Date())'

```{r include=FALSE,echo=FALSE}
require(tidyverse)

```

<!-- We recommend you use git branches -- create a separate branch for each major section i.e. Introduction, Methods, Results, Inferential Results, and Discussion and Conclusions - leave the YAML block untouched until the final merge where you put in your own name !-->
<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

# Introduction

 At the first day of class there are 35 students in Math Statistics class and professor Brownlow always proposes this bet to his students "I will wager $2 to your bet of $1 that at least two people in today's class have  the same birthday.  He tells me he has made that bet 1137 times so far. Where do you think his profits are? Discuss this in a markdown document.

# Methods

<!--Decide on your methods:  In this section explain the approach you will take to attack the issue --- how will you decide on a likely estimate of professor Brownlow's earnings or losses after 1137 bets. Also explain how you construct a 95% confidence interval about your estimate of his winnings !-->

The way I will do this is sampling a 1,137 bets by 35 birthdays by getting the sample from "unique" and then if the number is less than 35 then Brownlow gets $1 and if the answer comes out 35 then brownlow loses $2.  

# Profit Estimate


<!--Explain and display the results of your method of coming up with the estimate of professor Brownlows betting!-->

First we create the year data and a vector to contain samples.


```{r}
Bdays = 1:365
Bsamples = vector ('numeric')
TotalDollars = 0
saveDollars=vector('numeric')

```

run the simulation 1137 times. 

```{r}
for(loop in 1:1000){
TotalDollars=0
for(i in 1:1137) {
Bsamples = sample(Bdays,35, replace=TRUE)
if (length(unique(Bsamples)) == 35) {
TotalDollars = TotalDollars -2
} else{
TotalDollars = TotalDollars +1
}
}
saveDollars[loop] = TotalDollars
}
hist(saveDollars)
print(mean(saveDollars))

```


# Confidence interval of Brownlows earning

<!--Explain and display your method of coming up with a 95% confidence interval of  professor Brownlows-->

Using the sampling I found the average amount made was $503

```{r}
stdevDollars = sd(saveDollars)
meanDollars= mean(saveDollars)
CI = c(meanDollars-2*stdevDollars, meanDollars+2*stdevDollars)

print(CI)
```


# Discussion and Conclusion

<!--Discussion and conclusion here.  If professor Brownlow is consistantly making or losing money how could he change his payout so that his profits center on zero?  Also discuss what size his class should be in order to have his current scheme balance at zero profit.!-->

To adjust the payout, Brownlow could change his win to +1 and his losses to -4.50 which would center it at about zero. To adjust the class size, it would have to be about 28 or 29, then his payout woud be centered around zero.